Paper_analyses

### 2021-08-24 IAPS_PREPROCESSING_2021_1.Rmd
t

# \why?
tmp.df4<- tmp.df4%>%
  group_by(ssid, tNo, text)%>%
  mutate(stdev_gaze_x = sd(gaze_x_cor_pix, na.rm = TRUE))%>%
  mutate(stdev_gaze_y = sd(gaze_y_cor_pix, na.rm = TRUE))

@@

tmp.df4_sum_full_bio_hr_self_parsed
write_csv(tmp.df4_sum_full_bio_hr_self_parsed, 'tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv')
write_csv(tmp.df4, 'tmp.df4_timeseries_345_356.csv')
```

>>>>

# \why?
unique(tmp.df4$text)

tmp.df4<- tmp.df4%>%
  group_by(ssid, tNo, text)%>%
  mutate(stdev_gaze_x = sd(gaze_x_cor_pix, na.rm = TRUE))%>%
  mutate(stdev_gaze_y = sd(gaze_y_cor_pix, na.rm = TRUE))

@@

tmp.df4_sum_full_bio_hr_self_parsed
write_csv(tmp.df4_sum_full_bio_hr_self_parsed, 'tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv')
write_csv(tmp.df4, 'tmp.df4_timeseries_345_356.csv')

tmp.df4_sum_full_bio_hr_self_parsed$screencontent_no

tmp.df4_sum_full_bio_hr_self_parsed$TAS
tmp.df4_sum_full_bio_hr_self_parsed %>%
  subset(screencontent_no>2)%>%
  group_by(ssid)%>%
  summarise_if(is.numeric,mean, na.rm = TRUE)%>%
  ggplot(aes(Age,sdev_gazesum))+
  geom_point()+
  geom_smooth(method = lm, se = F)

### 2021-08-24 Paper_Analyses_subj_obje_arousal.Rmd
t

```{r}
options(contrasts = c("contr.sum","contr.poly"))
options(scipen = 999)

>>>>

```{r}
db_full4new$screencontent_no
db_full4new %>%
  subset(screencontent_no ==4)%>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean,na.rm = TRUE)%>%
  ggplot(aes(TAS, fix_count))+
  geom_point()+
  geom_smooth(method = lm, se = F)+
  ggpubr::stat_cor()

db_full4new %>%
  subset(screencontent_no > 2)%>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean,na.rm = TRUE)%>%
  ggplot(aes(TAS, fix_count))+
  geom_point()+
  geom_smooth(method = lm, se = F)+
  ggpubr::stat_cor()

options(contrasts = c("contr.sum","contr.poly"))
options(scipen = 999)
